Do we need detailed demographic data to forecast plant population responses to climate change?

### 2015-06-05 manuscript/manuscript.tex
updates ms with climate sensitivity figure

We performed one-step-ahead forecasts to compare the two models (IPM
vs.~QBM). We did not use the random year effects for these forecasts.
Thus, beyond the effect of genet size or quadrat cover, only the climate
covariates could affect expect plant cover. The models had similar
accuracy ($\rho$, correlation between observations and mean prediction
from 100 forecasts) across all species (Table 1). However, the IPM had
significantly lower overall error (MAE, mean absolute error) for two
species (\emph{H. comita} and \emph{P. smithii}), and in no case did the
QBM significantly outperform the IPM (Table 1).

@@

The IPM MAE is significantly lower for HECO ($p = 3.3 \times 10^{-10}$)
and POSE ($p = 0.00013$). MAEs are statisticially similar between models
for BOGR and PASM.

>>>>

We performed one-step-ahead forecasts to compare the two models (IPM
vs.~QBM). We did not use the random year effects for these forecasts.
Thus, beyond the effect of genet size or quadrat cover, only the climate
covariates could affect expect plant cover. The models had similar
accuracy (\(\rho\), correlation between observations and mean prediction
from 100 forecasts) across all species (Table 1). However, the IPM had
significantly lower overall error (MAE, mean absolute error) for two
species (\emph{H. comita} and \emph{P. smithii}), and in no case did the
QBM significantly outperform the IPM (Table 1).

@@

The IPM MAE is significantly lower for HECO
(\(p = 3.3 \times 10^{-10}\)) and POSE (\(p = 0.00013\)). MAEs are
statisticially similar between models for BOGR and PASM.
